RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-12-29 manuscripts/manuscript.Rmd
Moves down metadata section from earlier position.

>>>>

NeXML allows attaching metadata to any data element, and even to
metadata themselves. At the level of the document as a whole or the
phylogeny, metadata can provide bibliographic and provenance
information, for example about the study as part of which the
phylogeny was generated or applied, and with which methods it was
generated. In the form of annotations, metadata can also be attached
to very specific elements of the data, such as individual OTUs, nodes,
or even edges of the phylogeny.
